POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2024-02-26 challenges/coinduction.tex
A few minor corrections.

This challenge is  about the mechanisation of proofs concerning processes wih infinite behaviours.
This is usually connected to \emph{coinductive} definitions where an infinite
structure is defined as the greatest fixed point of a recursive
definition.
%
Coinduction is a technique for defining and proving properties of
such infinite structures.

@@

\subsubsection{Semantics.} We choose to give an LTS semantics for this
challenge.

>>>>

This challenge is about the mechanisation of proofs concerning processes with infinite behaviours.
This is usually connected to \emph{coinductive} definitions where an infinite
structure is defined as the greatest fixed point of a recursive
definition.
%
Coinduction is a technique for defining and proving properties of
such infinite structures.

@@

\subsubsection{Semantics.} We choose to give a labelled transition system semantics for this
challenge.
